Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-04-10 tex/MesnardoBarba2019.tex
Add comments about p2p results

Point-to-point MPI benchmarks from the Ohio State University Micro-Benchmarks\footnote{OSU Micro-Benchmarks (version 5.6): \url{http://mvapich.cse.ohio-state.edu/benchmarks/}} suite ran on Microsoft Azure and Colonial One to investigate performance in terms the latency and bandwidth.
The latency test is carried out in a ping-pong fashion and measures the time elapsed to get a response; the sender sends a message with a certain data size and wait for the receiver to send back the message with the same data size.
The bandwidth test measures the maximum sustained rate that can be achieved on the network; it consists in having the sender sends a fixed number of messages to a receiver that replies only after receiving all of them.
The tests ran on \texttt{NC24r} nodes on Azure and \texttt{Ivygpu} nodes on Colonial One, all of them featuring a network interface for RDMA (Remote Direct Memory Access) connectivity to communicate over an InfiniBand network.
(RDMA allows direct access to a remote's memory without involving the operating system of the host and remote.)
Fig. \ref{fig:osu_benchmarks} reports the mean latencies and bandwidths obtained over $5$ repetitions on both platforms.

>>>>

Point-to-point MPI benchmarks from the Ohio State University Micro-Benchmarks\footnote{OSU Micro-Benchmarks (version 5.6): \url{http://mvapich.cse.ohio-state.edu/benchmarks/}} suite ran on Microsoft Azure and Colonial One to investigate performance in terms the latency and bandwidth.
The latency test is carried out in a ping-pong fashion and measures the time elapsed to get a response; the sender sends a message with a certain data size and wait for the receiver to send back the message with the same data size.
The bandwidth test measures the maximum sustained rate that can be achieved on the network; it consists in having the sender sends a fixed number of messages to a receiver that replies only after receiving all of them.
The tests ran on \texttt{NC24r} nodes on Azure and \texttt{Ivygpu} nodes on Colonial One, all of them featuring a network interface for RDMA (Remote Direct Memory Access) connectivity to communicate over an InfiniBand network.
(RDMA allows direct access to a remote's memory without involving the operating system of the host and remote.)
Fig. \ref{fig:osu_benchmarks} reports the mean latencies and bandwidths obtained over $5$ repetitions on both platforms.
For small message sizes, the averaged latency on Colonial One and Azure are $1.75$ and $1.95 \mu s$, respectively.
As the message size increases, the latency becomes smaller on Azure compared to Colonial One.
The maximum sustained bandwidth rates for Colonial One and Azure are on average $4.5$ and $5.6 GB/s$, respectively.
For all message sizes, a higher bandwidth rates was achieved on Azure.
Over the last few years, Microsoft Azure has improved its HPC solution to provide networking capabilities that are comparable or even better than our 6-year-old university-managed cluster.
